AHABus \& FCORE: A Modular Bus System for High-Altitude Balloon Missions

### 2017-04-25 paper.tex
Proof read acknowledgements

I would like to thank my supervisor, Dr. Ian Ferguson, for the support and
insight he gave throughout this research project, and as Dr. Natalie Coull for
her advice during the proposal phase of the project.

>>>>

I would like to thank my supervisor, Dr. Ian Ferguson, for the support and insight he gave throughout this research project, as well as Dr. Natalie Coull for her advice during the proposal phase, Caitlin Smith and Chloë Smyth for their support over the duration of the project.
